---
title: "user2017"
author: "Tobias Romar"
date: "5 juli 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##robets forecasting time series with robust exponential smoothing methods with trend and seasonality

- Trend, seasonality and error component
- Additive or multiplicative
- Base case model to use:

```{r ets}
library(forecast)
model <-  ets(1:10)
```

- New suggested model suggested that is not that sensitive to outliers

```{r robets}
library(robets)
model <-  robets(1:10)
```


##A benchmark of Open Source Tools for Machine Laearning from R

- Mention the importance of just increasing RAM and then you can do many calculation in R
- 90 percent of the analysis is done with data up to 10 million records
- Which alorithms to adopt for that case?
- Random Forest, Ann and boosting
- R packaes, python scikit learn and H20 together 80 percent of machine learning
- Github: szilard/benchm-ml
- xgboost performing best for random forest (h20 also good)
- lightgbm fastest for boosted models
- airline data boosting beating deep learning
- R Keras package released some weeks ago
- main conclusion: get some value from data - use best tools


##Interacting with databases from shiny

- Use shiny as GUI to fill in data in a db
- Useful packages: DBI, odbc, dplyr, pool
- Realtional databases and NoSQL
- DBI - Interacts with the database from R. Possible to write to db - watch ip for malfunctions, e.g. delate table
- odbc - independent of operating system (standrs api to interact with databases). Looks similar to DBI.
- dplyr - the point here is to use dplyr insated of SQL to manipulate the data
- pool - creates a pool of connections, local connection, mainly important for shiny apps, poolConnect instaed of DBIconnect  & DBI close
- A GRUD APP


##ShinyProxy

- Way to host shiny apps on a server
- How to configure the shiny application on the server
- Possible to set up different accounts with different permissions
- Possible to collect user statistics 
- European commission has requested a range of shiny applications
- Main conclusion: deploy locally developed shiny apps on the server


##ShinyProxy

- Developing and deploying large scale Shiny applications for non-life insurance
- FRISS - generates a risk score based on different data sources
- Uses shiny applications to analyse and present the data
- Uses OPENCPU for statistical modelling
- Make a map apps with Leaflet
- Network plots to identify fraud (how each claim is related)
- Create interactive apps with shiny + htmlwidgets
- html templates
- Docker
- Octopus
- In general: Split big apps into moduls


####Lunch Break...

##Stream processing with R in AWS

- AWR, AWR.KMS, AWR.Kinesis (R Packages)
- Use R for stream processing due to simplicity, not 100 rows of Jave code to change date format
- Potentially worth to pay for infrastructure (AWS)
- Kinesis -> stream processing data. Continously filter the data you want, e.g. username for twitter data
- Example how to read data from Kinesis, library(AWS.Kinesis) #cannot run in RStudio
- Specific file needs to be written to execute
- flight data: library(nycflights13)
- Dockerize the application in order to run it everywhere
- Amazon has ECR in order to store the docker file

##Architectural Elements Enabling R for Big Data

- Big data definition: when regular applocation can´t deal with it
- We want to use R for everything
- With R, data need to fit into RAM
- When data gets bigger -> offload to processing to powerful backends
- Oracle in collaboration with Hadoop and Spark etc.
- ORAAH, sparklyr
- Data and Task Parallelism, example ore.tableApply()
- Conclusion: Leverage powerful back-ends to do the heavy work
- Oracle R Advanced Analytics for Hadoop
- Oracle database pitch!

##Beyond  Prototyping: Best practises for R in critical production environments

- Production, Test & Development
- Version Control - Branch Strategy between the above
- Continuous integration - Checking if updated in in Github automatically
- Package management - Problems when different versions of packages -> install packages to the projects or: 
- centralized Package Management -  LRAN --> Data Science Admin

##Implementing Predictive Analytics projects in corporate environmnets

- Which kind of projects, different corporate environments and best implementations?
- Online marketing, CRM & BI/Reporting
- SQL, R Markdown & data processing and Model train and test in R
- Case 1: Banking Industry - scoring algorithmn to make recommendations on product to offer. R in backend
- Case 2: Inbound Callcenter - demand forecats - scheduled R jobs to update the model
- Case 3: conversion score for real time bidding - auction for ad publishing on webpages


##Neural Embeddings and NLP with R and Spark

- Neural Embeddings - going beyond word vectors
- Context-Based Representation - How we use words
- Semantic meaning - the meaning
- GHTorrent Dataset
- Sequence to Sequence Learning : Encoder-Decoder Models
- Seq2Seq
- Trainig with a LSTM
- Implementation in CNTK




















- 